---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# flmtools

<!-- badges: start -->
[![Travis Build Status](https://travis-ci.com/atyre2/flmtools.svg?branch=master)](https://travis-ci.com/atyre2/flmtools)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/atyre2/flmtools?branch=master&svg=true)](https://ci.appveyor.com/project/atyre2/flmtools)
[![codecov](https://codecov.io/gh/atyre2/flmtools/branch/master/graph/badge.svg)](https://codecov.io/gh/atyre2/flmtools)

<!-- badges: end -->

Functions for working with Functional Linear Models fit by package mgcv

## Installation

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("atyre2/flmtools")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(flmtools)
test <- lagData(env_data, response_data, unit = "month", 6, 24, "envVar")
dim(test$envVar_6_24)
test$envVar_6_24[1:5,1:5]
```

## Code of Conduct

 Please note that the 'flmtools' project is released with a
  [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
  By contributing to this project, you agree to abide by its terms.
